---
title: "Statistical analyses"
author: "An Bui"
date: "11/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(tidyverse)
library(vegan)
library(here)
library(janitor)
```

### Soil characteristics

#### a. Data
```{r}
soil <- read_csv(here::here("data", "soil_data.csv"))
```

#### b. Analysis of variance
```{r}
# nitrogen
n_aov <- aov(N_p ~ site, data = soil) 
summary(n_aov)
TukeyHSD(n_aov)

# carbon
c_aov <- aov(C_p ~ site, data = soil)
summary(c_aov)
TukeyHSD(c_aov)

# phosphorus
p_aov <- aov(P ~ site, data = soil)
summary(p_aov)
TukeyHSD(p_aov)

# organic matter
om_aov <- aov(OM ~ site, data = soil)
summary(om_aov)
TukeyHSD(om_aov)

# total exchangeable cations
TEC_aov <- aov(TEC ~ site, data = soil)
summary(TEC_aov)
TukeyHSD(TEC_aov)

# ppm NO3
no3_aov <- aov(NO3_ppm ~ site, data = soil)
summary(no3_aov)
TukeyHSD(no3_aov)

# ppm NH4
nh4_aov <- aov(NH4_ppm ~ site, data = soil)
summary(nh4_aov)
TukeyHSD(nh4_aov)

# gravimetric water content
moisture_aov <- aov(GravWContent ~ site, data = soil)
summary(moisture_aov)
TukeyHSD(moisture_aov)

# pH
ph_aov <- aov(pH ~ site, data = soil)
summary(ph_aov)
TukeyHSD(ph_aov)
```

### Fungal community composition

#### a. Data
```{r}
# OTU paths
otu_paths <- read_csv(here::here("data", "otu_paths.csv"))

# fungal abundance
fun_abund <- read_csv(here::here("data", "fungal_abundance.csv"))
```

#### b. Species richness
```{r}
# create a vector of OTUs that pass the quality filter
keep_these <- otu_paths %>% 
  # filter confidence_ranking to only include "highly probable" or "probable" matches
  filter(confidence_ranking != c("-", "Possible") & notes != "Unassigned") %>% 
  # extract OTUs as vector
  pull(OTU_ID) %>% 
  # add column names "tree" and "site" for easier downstream processing
  combine(c("tree", "site"), .)
```

```{r}
# create a dataframe of abundances for filtered OTUs
rich_df <- fun_abund[, keep_these] %>% 
  # make tree ID row names
  column_to_rownames("tree") %>% 
  # remove site column
  select(-site)

# create a dataframe of "metadata" - only tree ID and site type
rich_meta <- fun_abund[, keep_these] %>% 
  select(tree, site)

# calculate species richness
attach(rich_meta)

# use vegan::specpool() on abundance dataframe to calculate species richness for each tree
tree_rich <- specpool(rich_df, tree) %>% 
  # make row names a column called "tree"
  rownames_to_column("tree") %>% 
  # join with metadata dataframe
  full_join(rich_meta, .)

# calculate mean species richness per tree per site
rich_summary <- tree_rich %>% 
  # group dataframe by site
  dplyr::group_by(site) %>% 
  # calculate mean richness per tree per site
  dplyr::summarize(mean_rich = mean(Species))

# analysis of variance
rich_aov <- aov(Species ~ site, data = tree_rich)
summary(rich_aov)
TukeyHSD(rich_aov)
```

#### c. Species diversity
```{r}
# use vegan::diversity
shannondiv <- diversity(rich_df) %>% 
  # make results of diversity into dataframe
  enframe() %>% 
  # rename columns for ease of processing
  dplyr::rename(tree = name, 
                shan_div = value) %>% 
  # join with metadata dataframe
  full_join(rich_meta, .)

# calculate mean shannon diversity per tree per site
shannondiv_summary <- shannondiv %>% 
  dplyr::group_by(site) %>% 
  dplyr::summarize(mean_shandiv = mean(shan_div))

# analysis of variance
shandiv_aov <- aov(shan_div ~ site, data = shannondiv)
summary(shandiv_aov)
```

#### d. Non-metric Multidimensional Scaling (NMDS)

```{r functions}
# extract OTUs specific to a particular functional group
# functional groups include: symbiotrophs, ectomycorrhizae, and arbuscular mycorrhizae
otus <- function(func_group) {
  otu_paths %>% 
  dplyr::filter({{ func_group }} == "TRUE" & confidence_ranking != c("-", "Possible") & notes != "Unassigned") %>% 
  pull(OTU_ID) %>% 
  combine(c("tree", "site"), .) %>% 
  fun_abund[, .] %>% 
  # make sure that no rows have only 0 values (no samples have no symbio OTUs)
  # add up rows into new column called total
  dplyr::mutate(total = select(., 3:ncol(.)) %>% rowSums(na.rm = TRUE)) %>% 
  # filter out empty rows based on total
  dplyr::filter(total > 0) %>%
  # get rid of total column by selecting all other columns
  dplyr::select(-total)
}

# designate which columns are data and OTUs
# metadata
metadata <- function(dataframe) {
  dataframe %>% 
    dplyr::select(1:2)
}

# OTUs
OTU_matrix <- function(dataframe) {
  dataframe %>% 
    column_to_rownames("tree") %>% 
    dplyr::select(-(1:2))
}

# metaMDS function from vegan package
fungi_nmds <- function(dataframe) {
  metaMDS(dataframe, 
          # use Bray-Curtis dissimilarity
          distance = "bray", 
          # reduce to 2 dimensions
          k = 2, 
          # adds small positive value for 0 count
          zerodist = "add", 
          # maximum number of iterations
          maxit = 30)
}

# plot dataframe
plot_df <- function(nmds_out, meta_df) {
  # extract points from NMDS output
  as_tibble(nmds_out$points) %>% 
    # combine with metadata and put metadata first
    bind_cols(meta_df, .) %>% 
    # set levels
    dplyr::mutate(site = fct_relevel(site, c("arid", "intermediate", "mesic")))
}

# plot function
plot_NMDS <- function(dataframe) {
  ggplot(dataframe, aes(x = MDS1, y = MDS2, 
                        fill = site, shape = site)) +
    geom_point(size = 4, stroke = 0.75, alpha = 0.8) +
    scale_shape_manual(values = c(24, 21, 22)) +
    scale_fill_manual(values = c("white", "lightgrey", "black")) +
    stat_ellipse() +
    coord_fixed() +
    theme(plot.background = element_rect("white"),
          panel.background = element_rect("white"),
          panel.grid = element_line("grey90"),
          axis.line = element_line("gray25"),
          axis.text = element_text(size = 12, color = "gray25"),
          axis.title = element_text(color = "gray25"),
          legend.text = element_text(size = 12))
}
```

```{r}
all_meta <- metadata(fun_abund)
all_matrix <- OTU_matrix(fun_abund[, keep_these])

all_NMDS <- fungi_nmds(all_matrix)
all_df <- plot_df(all_NMDS, all_meta)
all_plot <- plot_NMDS(all_df) + labs(title = "All fungi")
all_plot
```

```{r}
all_perm <- adonis(all_matrix ~ site, data = all_meta, method = "bray")
all_perm
```

```{r}
symbio <- otus(tm_symbiotroph)

symbio_meta <- metadata(symbio)
symbio_matrix <- OTU_matrix(symbio)

symbio_NMDS <- fungi_nmds(symbio_matrix)

symbio_df <- plot_df(symbio_NMDS, symbio_meta)

symbio_plot <- plot_NMDS(symbio_df) + labs(title = "Symbiotrophs")
symbio_plot
```

```{r}
symbio_perm <- adonis(symbio_matrix ~ site, data = symbio_meta, method = "bray")
symbio_perm
```

```{r}
ectos <- otus(g_ectomycorrhizal)

ecto_meta <- metadata(ectos)
ecto_matrix <- OTU_matrix(ectos)

ecto_NMDS <- fungi_nmds(ecto_matrix)

ecto_df <- plot_df(ecto_NMDS, ecto_meta)

ecto_plot <- plot_NMDS(ecto_df) + labs(title = "Ectomycorrhizae")
ecto_plot
```

```{r}
ecto_perm <- adonis(ecto_matrix ~ site, data = ecto_meta, method = "bray")
ecto_perm
```

```{r}
amf <- otus(g_arbuscular_mycorrhizal)

amf_meta <- metadata(amf)
amf_matrix <- OTU_matrix(amf)

amf_NMDS <- fungi_nmds(amf_matrix)

amf_df <- plot_df(amf_NMDS, amf_meta)

amf_plot <- plot_NMDS(amf_df) + labs(title = "Arbuscular mycorrhizae")
amf_plot
```

```{r}
amf_perm <- adonis(amf_matrix ~ site, data = amf_meta, method = "bray")
amf_perm
```

### Community convergence

For ease of use, example code is for bootstrapping the total fungal community. This repeats for symbiotrophs, arbuscular mycorrhizae (AMF), and ectomycorrhizae. The final section (c. Final data) includes the summarized data for all 1000 bootstraps (mean, standard deviation, and standard error).

#### a. Determine number of OTUs for downsampling
```{r}
# which functional group has the lowest number of OTUs?
all_n <- ncol(all_matrix)
# 1562
symb_n <- ncol(symbio_matrix)
# 553
AMF_n <- ncol(amf_matrix)
# 191
ecto_n <- ncol(ecto_matrix)
# 91

# store ecto_n as lowest_n
lowest_n <- ecto_n
```

#### b. Set up bootstrapping by creating NMDS objects
```{r eval = FALSE}
# make an empty list into which to put the output of the loop
list_nmds <- list()

# for every object in the iteration
for(i in 1:1000) {
  # resample lob_matrix for the lowest_n OTUs (91)
  resample <- all_matrix %>% sample(lowest_n)
  # perform NMDS on the resampled community
  do_nmds <- metaMDS(resample, distance = "bray", k = 2, zerodist = "add", maxit = 30)
  
  # put output into empty list
  list_nmds[[i]] <- do_nmds
}
```

```{r}
# find site centroid using vegan::ordihull()
centroid <- function(meta, nmds_object) {
  with(meta, ordihull(nmds_object, site, label = TRUE))
}

# get centroid coordinates into a dataframe
find_coords <- function(centroid_object, tax_group) {
  tibble::as_tibble(summary(centroid_object)) %>% 
    dplyr::mutate(colname = c("MDS1", "MDS2", "area")) %>% 
    tibble::column_to_rownames("colname") %>% 
    t() %>% 
    tibble::as_tibble() %>% 
    dplyr::mutate(site = c("arid", "intermediate", "mesic"),
                  type = tax_group)
}

# distance between points
dist_fun <- function(point1, point2) {
  sqrt((point1$MDS1 - point2$MDS1)^2 + (point1$MDS2 - point2$MDS2)^2)
}
```

The final product of the following loop is a list of dataframes, each of which is one iteration of the loop. Its contents are the calculation (Euclidean distance between a community and its site centroid) for each tree.
```{r eval = FALSE}
list_calc_all <- list()

for(i in 1:1000) {
  # find distance between centroids
  # 1. find centroid coordinates
  cent_coords <- centroid(all_meta, list_nmds[[i]])
  # 2. turn into data frame
  centroid_df <- find_coords(cent_coords, "all")
  # 3. get things into their own dataframe by site
  arid_cent <- centroid_df %>% filter(site == "arid")
  int_cent <- centroid_df %>% filter(site == "intermediate")
  mes_cent <- centroid_df %>% filter(site == "mesic")
  # 4. find distance between centroids
  ai_dist <- dist_fun(arid_cent, int_cent)
  am_dist <- dist_fun(arid_cent, mes_cent)
  im_dist <- dist_fun(int_cent, mes_cent)
  
  # find distance between point and centroid
  # 1. find coordinates for each point and join with metadata
  tree_coords <- scores(list_nmds[[i]]) %>% as.data.frame() %>% 
    rownames_to_column("tree") %>% 
    full_join(all_meta, ., by = "tree")
  # 2. put tree coordinates together with the centroid coordinates
  joined_coords <- full_join(tree_coords, centroid_df, by = "site") %>% 
    dplyr::rename(cent_MDS1 = MDS1, cent_MDS2 = MDS2) %>% 
    mutate(dist_t2c = sqrt((cent_MDS1 - NMDS1)^2 + (cent_MDS2 - NMDS2)^2))
  
  # do the calculation
  # 1. arid-int
  arid_int <- joined_coords %>% 
    filter(site == "arid") %>% 
    mutate(calc = ai_dist/dist_t2c,
           comp = "arid-int")
  # 2. arid-mesic
  arid_mesic <- joined_coords %>% 
    filter(site == "arid") %>% 
    mutate(calc = am_dist/dist_t2c,
           comp = "arid-mesic")
  # 3. int-mesic
  int_mesic <- joined_coords %>% 
    filter(site == "intermediate") %>% 
    mutate(calc = im_dist/dist_t2c,
           comp = "int-mesic") 
  # 4. int-arid
  int_arid <- joined_coords %>% 
    filter(site == "intermediate") %>% 
    mutate(calc = ai_dist/dist_t2c,
           comp = "int-arid") 
  # 5. mesic-arid
  mes_arid <- joined_coords %>% 
    filter(site == "mesic") %>% 
    mutate(calc = am_dist/dist_t2c,
           comp = "mes-arid") 
  # 6. mesic-int
  mes_int <- joined_coords %>% 
    filter(site == "mesic") %>% 
    mutate(calc = im_dist/dist_t2c,
           comp = "mes_int")
  
  # join all those together
  final_df <- bind_rows(arid_int, arid_mesic, int_mesic, int_arid, mes_arid, mes_int) %>% 
    select(tree, site, calc, comp) %>% 
    # group_by(site, comp) %>% 
    mutate(resample_n = i)
  
  list_calc_all[[i]] <- final_df
}
```

#### c. Final data
```{r}
boot_data <- read_csv(here::here("data", "boot_data-1000.csv"))
```

### Ectomycorrhizal functional traits

```{r}
ecto_OTU_traits <- read_csv(here::here("data", "ecto_OTU_traits.csv"))
```

```{r}
# create a dataframe where OTUs are in rows, and samples are in columns
transposed <- fun_abund %>% 
  select(-site) %>%
  column_to_rownames("tree") %>% 
  t() %>% 
  as.data.frame() %>% 
  rownames_to_column("OTU_ID")

# extract metadata
fun_metadata <- fun_abund %>% 
  select(1, 2)

# create a dataframe where trees are in rows and counts for each functional trait are in columns
sum_traits <- inner_join(ecto_OTU_traits, transposed) %>% 
  pivot_longer(4:57, names_to = "tree", values_to = "count") %>% 
  dplyr::group_by(tree, trait, type) %>% 
  dplyr::summarize(sum = sum(count)) %>% 
  full_join(fun_metadata, ., by = "tree") %>% 
  ungroup() %>% 
  dplyr::select(tree, site, type, sum) %>% 
  pivot_wider(names_from = "type", values_from = "sum") %>% 
  clean_names()
```

#### a. Exploration type

```{r}
# create contingency tables for each trait
chitable_et <- sum_traits %>% 
  dplyr::select(site, long_distance, medium, short) %>% 
  group_by(site) %>% 
  summarize_if(is.numeric, sum) %>% 
  column_to_rownames("site")

chitable_rhizo <- sum_traits %>% 
  dplyr::select(site, contains("r_")) %>% 
  group_by(site) %>% 
  summarize_if(is.numeric, sum) %>% 
  column_to_rownames("site")
```

```{r}
# chi square test
chitest_et <- stats::chisq.test(chitable_et)
chitest_et

chitest_rhizo <- stats::chisq.test(chitable_rhizo)
chitest_rhizo
```