---
title: "Statistical analyses"
author: "An Bui"
date: "11/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
# general use packages
library(tidyverse)
library(janitor)
library(here)
library(rlang)

# community composition analyses
library(vegan)

# community convergence 
library(usedist)

# model selection
library(ecodist)
library(MuMIn)
library(gt)

# library(geosphere)
```

### Soil characteristics

#### a. Data
```{r}
soil <- read_csv(here::here("data", "soil_data.csv"))
```

#### b. Analysis of variance
```{r}
# nitrogen
n_aov <- aov(N_p ~ site, data = soil) 
summary(n_aov)
TukeyHSD(n_aov)

# carbon
c_aov <- aov(C_p ~ site, data = soil)
summary(c_aov)
TukeyHSD(c_aov)

# phosphorus
p_aov <- aov(P ~ site, data = soil)
summary(p_aov)
TukeyHSD(p_aov)

# organic matter
om_aov <- aov(OM ~ site, data = soil)
summary(om_aov)
TukeyHSD(om_aov)

# total exchangeable cations
TEC_aov <- aov(TEC ~ site, data = soil)
summary(TEC_aov)
TukeyHSD(TEC_aov)

# ppm NO3
no3_aov <- aov(NO3_ppm ~ site, data = soil)
summary(no3_aov)
TukeyHSD(no3_aov)

# ppm NH4
nh4_aov <- aov(NH4_ppm ~ site, data = soil)
summary(nh4_aov)
TukeyHSD(nh4_aov)

# gravimetric water content
moisture_aov <- aov(GravWContent ~ site, data = soil)
summary(moisture_aov)
TukeyHSD(moisture_aov)

# pH
ph_aov <- aov(pH ~ site, data = soil)
summary(ph_aov)
TukeyHSD(ph_aov)
```

### Fungal community composition

#### a. Data
```{r}
# OTU paths
otu_paths <- read_csv(here::here("data", "otu_paths.csv"))

# fungal abundance
fun_abund <- read_csv(here::here("data", "fungal_abundance.csv"))
```

#### b. Species richness
```{r}
# create a vector of OTUs that pass the quality filter
keep_these <- otu_paths %>% 
  # filter confidence_ranking to only include "highly probable" or "probable" matches
  filter(confidence_ranking != c("-", "Possible")) %>% 
  # extract OTUs as vector
  pull(OTU_ID) %>% 
  # add column names "tree" and "site" for easier downstream processing
  vctrs::vec_c(c("tree", "site"), .)
```

```{r}
# create a dataframe of abundances for filtered OTUs
rich_df <- fun_abund[, keep_these] %>% 
  # make tree ID row names
  column_to_rownames("tree") %>% 
  # remove site column
  select(-site)

# create a dataframe of "metadata" - only tree ID and site type
rich_meta <- fun_abund[, keep_these] %>% 
  select(tree, site)

# calculate species richness
attach(rich_meta)

# use vegan::specpool() on abundance dataframe to calculate species richness for each tree
tree_rich <- specpool(rich_df, tree) %>% 
  # make row names a column called "tree"
  rownames_to_column("tree") %>% 
  # join with metadata dataframe
  full_join(rich_meta, .)

# calculate mean species richness per tree per site
rich_summary <- tree_rich %>% 
  # group dataframe by site
  dplyr::group_by(site) %>% 
  # calculate mean richness per tree per site
  dplyr::summarize(mean_rich = mean(Species))

# analysis of variance
rich_aov <- aov(Species ~ site, data = tree_rich)
summary(rich_aov)
TukeyHSD(rich_aov)
```

#### c. Species diversity
```{r}
# use vegan::diversity
shannondiv <- diversity(rich_df) %>% 
  # make results of diversity into dataframe
  enframe() %>% 
  # rename columns for ease of processing
  dplyr::rename(tree = name, 
                shan_div = value) %>% 
  # join with metadata dataframe
  full_join(rich_meta, ., by = "tree")

# calculate mean shannon diversity per tree per site
shannondiv_summary <- shannondiv %>% 
  dplyr::group_by(site) %>% 
  dplyr::summarize(mean_shandiv = mean(shan_div))

# analysis of variance
shandiv_aov <- aov(shan_div ~ site, data = shannondiv)
summary(shandiv_aov)
```

#### d. Non-metric Multidimensional Scaling (NMDS)

```{r functions}
# extract OTUs specific to a particular functional group
# functional groups include: symbiotrophs, ectomycorrhizae, and arbuscular mycorrhizae
otus <- function(func_group) {
  otu_paths %>% 
  dplyr::filter({{ func_group }} == "TRUE" & confidence_ranking != c("-", "Possible")) %>% 
  pull(OTU_ID) %>% 
  combine(c("tree", "site"), .) %>% 
  fun_abund[, .] %>% 
  # make sure that no rows have only 0 values (no samples have no symbio OTUs)
  # add up rows into new column called total
  dplyr::mutate(total = select(., 3:ncol(.)) %>% rowSums(na.rm = TRUE)) %>% 
  # filter out empty rows based on total
  dplyr::filter(total > 0) %>%
  # get rid of total column by selecting all other columns
  dplyr::select(-total)
}

# designate which columns are data and OTUs
# metadata
metadata <- function(dataframe) {
  dataframe %>% 
    dplyr::select(1:2)
}

# OTUs
OTU_matrix <- function(dataframe) {
  dataframe %>% 
    column_to_rownames("tree") %>% 
    dplyr::select(-(1:2))
}

# metaMDS function from vegan package
fungi_nmds <- function(dataframe) {
  metaMDS(dataframe, 
          # use Bray-Curtis dissimilarity
          distance = "bray", 
          # reduce to 2 dimensions
          k = 2, 
          # adds small positive value for 0 count
          zerodist = "add", 
          # maximum number of iterations
          maxit = 30)
}

# plot dataframe
plot_df <- function(nmds_out, meta_df) {
  # extract points from NMDS output
  scores(nmds_out, display = c("sites")) %>% 
    as.data.frame() %>% 
    # combine with metadata and put metadata first
    bind_cols(meta_df, .) %>% 
    # set levels
    mutate(site = fct_relevel(site, c("arid", "intermediate", "mesic")))
}

# plot function
plot_NMDS <- function(dataframe) {
  ggplot(dataframe, aes(x = NMDS1, y = NMDS2, 
                        fill = site, shape = site)) +
    geom_point(size = 4, stroke = 0.75, alpha = 0.8) +
    scale_shape_manual(values = c(24, 21, 22)) +
    scale_fill_manual(values = c("white", "lightgrey", "black")) +
    stat_ellipse() +
    coord_fixed() +
    theme(plot.background = element_rect("white"),
          panel.background = element_rect("white"),
          panel.grid = element_line("grey90"),
          axis.line = element_line("gray25"),
          axis.text = element_text(size = 12, color = "gray25"),
          axis.title = element_text(color = "gray25"),
          legend.text = element_text(size = 12))
}
```

```{r}
all_meta <- metadata(fun_abund)
all_matrix <- OTU_matrix(fun_abund[, keep_these])

all_NMDS <- fungi_nmds(all_matrix)
all_df <- plot_df(all_NMDS, all_meta)
all_plot <- plot_NMDS(all_df) + labs(title = "All fungi")
all_plot
```

```{r}
all_perm <- adonis(all_matrix ~ site, data = all_meta, method = "bray")
all_perm
```

```{r}
symbio <- otus(tm_symbiotroph)

symbio_meta <- metadata(symbio)
symbio_matrix <- OTU_matrix(symbio)

symbio_NMDS <- fungi_nmds(symbio_matrix)

symbio_df <- plot_df(symbio_NMDS, symbio_meta)

symbio_plot <- plot_NMDS(symbio_df) + labs(title = "Symbiotrophs")
symbio_plot
```

```{r}
symbio_perm <- adonis(symbio_matrix ~ site, data = symbio_meta, method = "bray")
symbio_perm
```

```{r}
ectos <- otus(g_ectomycorrhizal)

ecto_meta <- metadata(ectos)
ecto_matrix <- OTU_matrix(ectos)

ecto_NMDS <- fungi_nmds(ecto_matrix)

ecto_df <- plot_df(ecto_NMDS, ecto_meta)

ecto_plot <- plot_NMDS(ecto_df) + labs(title = "Ectomycorrhizae")
ecto_plot
```

```{r}
ecto_perm <- adonis(ecto_matrix ~ site, data = ecto_meta, method = "bray")
ecto_perm
```

```{r}
amf <- otus(g_arbuscular_mycorrhizal)

amf_meta <- metadata(amf)
amf_matrix <- OTU_matrix(amf)

amf_NMDS <- fungi_nmds(amf_matrix)

amf_df <- plot_df(amf_NMDS, amf_meta)

amf_plot <- plot_NMDS(amf_df) + labs(title = "Arbuscular mycorrhizae")
amf_plot
```

```{r}
amf_perm <- adonis(amf_matrix ~ site, data = amf_meta, method = "bray")
amf_perm
```

```{r}
sapro <- otus(tm_saprotroph)

sapro_meta <- metadata(sapro)
sapro_matrix <- OTU_matrix(sapro)

sapro_NMDS <- fungi_nmds(sapro_matrix)

sapro_df <- plot_df(sapro_NMDS, sapro_meta)

sapro_plot <- plot_NMDS(sapro_df) + labs(title = "Saprotrophs")
sapro_plot
```

```{r}
sapro_perm <- adonis(sapro_matrix ~ site, data = sapro_meta, method = "bray")
sapro_perm
```

```{r}
patho <- otus(tm_pathotroph)

patho_meta <- metadata(patho)
patho_matrix <- OTU_matrix(patho)

patho_NMDS <- fungi_nmds(patho_matrix)

patho_df <- plot_df(patho_NMDS, patho_meta)

patho_plot <- plot_NMDS(patho_df) + labs(title = "Pathotrophs")
patho_plot
```

```{r}
patho_perm <- adonis(patho_matrix ~ site, data = patho_meta, method = "bray")
patho_perm
```

```{r}
# ericoid
ericoid <- otus(g_ericoid_mycorrhizal)

arid_ericoid_OTUs <- ericoid %>% 
  pivot_longer(contains("OTU_"), names_to = "OTU_ID", values_to = "counts") %>%
  filter(site == "arid" & counts > 0) %>% 
  pull(OTU_ID) %>% 
  unique() %>% 
  length()

int_ericoid_OTUs <- ericoid %>% 
  pivot_longer(contains("OTU_"), names_to = "OTU_ID", values_to = "counts") %>%
  filter(site == "intermediate" & counts > 0) %>% 
  pull(OTU_ID) %>% 
  unique() %>% 
  length()

mesic_ericoid_OTUs <- ericoid %>% 
  pivot_longer(contains("OTU_"), names_to = "OTU_ID", values_to = "counts") %>%
  filter(site == "mesic" & counts > 0) %>% 
  pull(OTU_ID) %>% 
  unique() %>% 
  length()
```

### Redundancy analysis
```{r}
# subset data to only include soil samples that can be attributed to bioinformatic data
soil_samples <- soil %>% 
  pull(tree) %>% 
  purrr::discard(.p = ~stringr::str_detect(., "X"))

subset_soil_samples <- all_matrix[soil_samples,]

soil_rda_df <- soil %>% 
  filter(tree %in% soil_samples) %>% 
  column_to_rownames("tree")

# model with only intercept
fungi_rda_mod0 <- rda(subset_soil_samples ~ 1, data = soil_rda_df)
# model with all parameters
fungi_rda_mod1 <- rda(subset_soil_samples ~ ., data = soil_rda_df)

# stepwise model selection
model_selection <- ordiR2step(fungi_rda_mod0, scope = formula(fungi_rda_mod1), R2scope = FALSE)
model_selection # best model only includes site
model_selection$anova

# assess significance of each parameter as a constraint on ordination
anova(fungi_rda_mod1, by = "term")
```

### Multiple regression on species richness

```{r}
richness_subset <- tree_rich %>% 
  filter(tree %in% soil_samples) %>% 
  select(tree, Species) %>% 
  full_join(., soil, by = "tree") %>%
  drop_na()

# all parameters
fungi_mr_all <- lm(Species ~ N_p + C_p + P + OM + TEC + NO3_ppm + NH4_ppm + pH + 
                 GravWContent + site, data = richness_subset, na.action = na.pass)

# using MuMIn
dredged <- dredge(fungi_mr_all)

model.sel(dredged) %>% filter(delta < 4) %>% 
  gt() %>% 
  tab_header(title = "all model subsets",
             subtitle = "Richness ~ parameters")
```

### Mantel tests
```{r}
sample_coords <- read_csv(here::here("data", "sample_coords.csv"))
```

```{r}
# 1. calculate distances
# fungi 
fungi_dist <- vegdist(all_matrix, method = "bray")

# geographic location
coord_dist <- sample_coords %>% 
  column_to_rownames("Tree_ID") %>% 
  dist(., method = "euclidean")

# soil characteristics
soil_dist <- soil_coords %>% 
  column_to_rownames("tree") %>% 
  select(N_p:GravWContent) %>% 
  dist(., method = "euclidean")

# samples with soil characteristics and geographic location
soil_coords <- full_join(soil, sample_coords, by = c("tree" = "Tree_ID")) %>% 
  na.omit() %>% 
  select(-site)

filt_coords_dist <- soil_coords %>% 
  column_to_rownames("tree") %>% 
  select(GPS_N_dd, GPS_W_dd) %>% 
  dist(., method = "euclidean")


# 2. put distances into vectors
# fungi
fungi_dist_vector <- as.vector(fungi_dist)
# geographic location
coord_dist_vector <- as.vector(coord_dist)
# soil
soil_dist_vector <- as_vector(soil_dist)
# samples with soil characteristics and geographic location
filt_coords_dist_vector <- as.vector(filt_coords_dist)

# 3. mantel correlograms
# using ecodist
fungi_ecodist_mantel <- ecodist::mantel(fungi_dist_vector ~ coord_dist_vector)
soil_ecodist_mantel <- ecodist::mantel(soil_dist_vector ~ filt_coords_dist_vector)

# Mantel correlograms
mgram1 <- mgram(fungi_dist_vector, coord_dist_vector)
mgram1_df <- mgram1$mgram %>% 
  as.data.frame() %>% 
  # fill points for significance
  mutate(fill_point = case_when(
    pval > 0.05 ~ "no_fill",
    pval < 0.05 ~ "fill"
  ))

mgram1_plot <- ggplot(mgram1_df, aes(x = lag, y = mantelr)) +
  geom_line(col = "lightgrey") +
  geom_segment(aes(x = 0, xend = 0.11, y = 0, yend = 0), linetype = "dashed") +
  geom_point(aes(shape = fill_point), size = 4, stroke = 1) +
  scale_shape_manual(values = c(16, 21)) +
  scale_x_continuous(limits = c(0, 0.11), expand = c(0, 0)) +
  scale_y_continuous(limits = c(-0.75, 0.7)) +
  labs(x = "Distance",
       y = "Mantel r",
       title = "Fungal OTUs") +
  theme_bw() +
  theme(plot.background = element_rect("white"),
              panel.background = element_rect("white"),
              panel.grid = element_line("grey90"),
              axis.line = element_line("gray25"),
              axis.text = element_text(size = 12, color = "gray25"),
              axis.title = element_text(color = "gray25"),
              legend.position = "none")
mgram1_plot

mgram2 <- mgram(soil_dist_vector, filt_coords_dist_vector)
mgram2_df <- mgram2$mgram %>% 
  as.data.frame() %>% 
  mutate(fill_point = case_when(
    pval > 0.05 ~ "no_fill",
    pval < 0.05 ~ "fill"
  ))

mgram2_plot <- ggplot(mgram2_df, aes(x = lag, y = mantelr)) +
  geom_line(col = "lightgrey") +
  geom_segment(aes(x = 0, xend = 0.11, y = 0, yend = 0), linetype = "dashed") +
  geom_point(aes(shape = fill_point), size = 4, stroke = 1) +
  scale_shape_manual(values = c(21)) +
  scale_x_continuous(limits = c(0, 0.11), expand = c(0, 0)) +
  scale_y_continuous(limits = c(-0.75, 0.7)) +
  labs(x = "Distance",
       y = "Mantel r",
    title = "Soil characteristics") +
  theme_bw() +
  theme(plot.background = element_rect("white"),
              panel.background = element_rect("white"),
              panel.grid = element_line("grey90"),
              axis.line = element_line("gray25"),
              axis.text = element_text(size = 12, color = "gray25"),
              axis.title = element_text(color = "gray25"),
              legend.position = "none")
mgram2_plot
```

### Community convergence

For ease of use, example code is for bootstrapping the total fungal community. This repeats for symbiotrophs, arbuscular mycorrhizae (AMF), and ectomycorrhizae. The final section (c. Final data) includes the summarized data for all 1000 bootstraps (mean, standard deviation, and standard error).

#### a. Filter OTUs 
```{r}
# OTUs to keep
keep_conv <- otu_paths %>% 
  filter(confidence_ranking != c("-", "Possible") & notes != "Unassigned") %>% 
  pull(OTU_ID) %>% 
  vctrs::vec_c(c("tree", "site"), .)

# select keep_conv from fun_abund
conv_OTUs <- fun_abund[, keep_conv]

# designate which columns are samples and OTUs
conv_meta <- metadata(conv_OTUs)

conv_matrix <- OTU_matrix(conv_OTUs)

# lists of trees at each site
arid_trees <- conv_meta %>% filter(site == "arid") %>% pull(tree)
int_trees <- conv_meta %>% filter(site == "intermediate") %>% pull(tree)
mes_trees <- conv_meta %>% filter(site == "mesic") %>% pull(tree)
```

#### b. Determine number of OTUs for downsampling
```{r}
# which functional group has the lowest number of OTUs?
all_n <- ncol(conv_matrix)
# 1562
symb_n <- ncol(symbio_matrix)
# 553
AMF_n <- ncol(amf_matrix)
# 191
ecto_n <- ncol(ecto_matrix)
# 91

# store ecto_n as lowest_n
lowest_n <- ecto_n
```

#### c. Do the calculation

The final product of the following loop is a list of dataframes, each of which is one iteration of the loop. Its contents are the calculation (Bray-Curtis distance between a community and its site centroid) for each tree.

```{r eval = FALSE}
# make an empty list into which to put the output of the loop
list_BCdist <- list() 
plot_list <- list()  
list_calc_all <- list() 

# for every object in the iteration
for(i in 1:1000) {
  ###### PART 1. RESAMPLE
  # resample conv_matrix for the lowest_n OTUs (91)
  resample <- conv_matrix %>% sample(lowest_n)
  # perform NMDS on the resampled community
  BCdist <- vegdist(resample, method = "bray")
  nmds <- metaMDS(BCdist, method = "bray")
  coords <- scores(nmds, by = "site") %>% 
    as.data.frame() %>% 
    rownames_to_column("tree") %>% 
    full_join(., conv_meta, by = "tree")
  plotted_full <- plot_NMDS(coords) + labs(title = i)
  
  # put output into empty list
  list_BCdist[[i]] <- BCdist
  plot_list[[i]] <- plotted_full
  
  ###### PART 2. do the calculation
  # 1. find distance between centroids
  arid_int <- dist_between_centroids(BCdist, arid_trees, int_trees)
  arid_mes <- dist_between_centroids(BCdist, arid_trees, mes_trees)
  int_mes <- dist_between_centroids(BCdist, int_trees, mes_trees)
  
  # 2. find distance between tree and site centroid
  tree_to_site <- dist_to_centroids(BCdist, conv_meta$site)
  
  arid_distances <- tree_to_site %>% 
    filter(Item %in% arid_trees & CentroidGroup == "arid") %>% 
    select(Item, CentroidDistance) %>% 
    rename("tree" = Item) %>% 
    deframe()
  
  int_distances <- tree_to_site %>% 
    filter(Item %in% int_trees & CentroidGroup == "intermediate") %>% 
    select(Item, CentroidDistance) %>% 
    rename("tree" = Item) %>% 
    deframe()
  
  mes_distances <- tree_to_site %>% 
    filter(Item %in% mes_trees & CentroidGroup == "mesic") %>% 
    select(Item, CentroidDistance) %>% 
    rename("tree" = Item) %>% 
    deframe()
  
  # 3. do the calculation
  # arid - intermediate
  arid_int_calc <- enframe(arid_int/arid_distances) %>% 
    mutate(btwn = "arid_int", site = "arid") %>% 
    rename("tree" = name, "calc" = value)
  
  # arid - mesic
  arid_mes_calc <- enframe(arid_mes/arid_distances) %>% 
    mutate(btwn = "arid_mes", site = "arid") %>% 
    rename("tree" = name, "calc" = value)
  # intermediate - mesic
  int_mes_calc <- enframe(int_mes/int_distances) %>% 
    mutate(btwn = "int_mes", site = "int") %>% 
    rename("tree" = name, "calc" = value)
  # intermediate - arid
  int_arid_calc <- enframe(arid_int/int_distances) %>% 
    mutate(btwn = "int_arid", site = "int") %>% 
    rename("tree" = name, "calc" = value)
  # mesic - arid
  mes_arid_calc <- enframe(arid_mes/mes_distances) %>% 
    mutate(btwn = "mes_arid", site = "mesic") %>% 
    rename("tree" = name, "calc" = value)
  # mesic - intermediate 
  mes_int_calc <- enframe(int_mes/mes_distances) %>% 
    mutate(btwn = "mes_int", site = "mesic") %>% 
    rename("tree" = name, "calc" = value)
  
  # join all those together
  list_calc_all[[i]] <- bind_rows(arid_int_calc, arid_mes_calc,
                                  int_mes_calc, int_arid_calc, 
                                  mes_arid_calc, mes_int_calc) %>% 
    mutate(resample_n = i)
}
```

#### d. Null model: communities with shuffled read counts

This code creates new community matrices where read counts are shuffled between OTUs, but absent OTUs remain absent. These matrices are then run through the same loop as the original communities to generate a convergence metric.
```{r}
# outer loop: create multiple simulated matrices
shuff_matrices <- list()
shuff_dfs <- list()

for(j in 1:50) {
  
  simu_list <- list() 
  
  # for every row (i.e. sample) in lob_matrix
  for(i in 1:nrow(conv_matrix)) {
    # subset a sample
    subset <- conv_matrix[i, 1:dim(conv_matrix)[2]]
    # add in dummy row
    dum <- rbind(subset, rep(1, ncol(conv_matrix)))
    # run permatswap
    ## switches around reads per OTU but keeps the absent OTUs absent
    run_null <- permatswap(dum, method = "swsh", fixedmar = "rows", shuffle = "samp", strata = NULL, mtype = "count", times = 1)
    sums <- as.data.frame(run_null$perm)
    # remove dummy list
    simu_list[[i]] <- (sums[1, ] + sums[2, ]) - 1
  }
  
  # bind holding list
  bind <- as.data.frame(do.call("rbind", simu_list))
  
  bind_df <- bind %>% 
    rownames_to_column("tree") %>% 
    full_join(conv_meta, ., by = "tree")
  
  shuff_matrices[[j]] <- bind
  shuff_dfs[[j]] <- bind_df
}
```

### Ectomycorrhizal functional traits

```{r}
ecto_OTU_traits <- read_csv(here::here("data", "ecto_OTU_traits.csv"))
```

```{r}
# create a dataframe where OTUs are in rows, and samples are in columns
transposed <- fun_abund %>% 
  select(-site) %>%
  column_to_rownames("tree") %>% 
  t() %>% 
  as.data.frame() %>% 
  rownames_to_column("OTU_ID")

# extract metadata
fun_metadata <- fun_abund %>% 
  select(1, 2)

# create a dataframe where trees are in rows and counts for each functional trait are in columns
sum_traits <- inner_join(ecto_OTU_traits, transposed) %>% 
  pivot_longer(4:56, names_to = "tree", values_to = "count") %>% 
  dplyr::group_by(tree, trait, type) %>% 
  dplyr::summarize(sum = sum(count)) %>% 
  full_join(fun_metadata, ., by = "tree") %>% 
  ungroup() %>% 
  dplyr::select(tree, site, type, sum) %>% 
  pivot_wider(names_from = "type", values_from = "sum") %>% 
  clean_names()
```

#### a. Exploration type

```{r}
# create contingency tables for each trait
chitable_et <- sum_traits %>% 
  dplyr::select(site, long_distance, medium, short) %>% 
  group_by(site) %>% 
  summarize_if(is.numeric, sum) %>% 
  column_to_rownames("site")

chitable_rhizo <- sum_traits %>% 
  dplyr::select(site, contains("r_")) %>% 
  group_by(site) %>% 
  summarize_if(is.numeric, sum) %>% 
  column_to_rownames("site")
```

```{r}
# chi square test
chitest_et <- stats::chisq.test(chitable_et)
chitest_et

chitest_rhizo <- stats::chisq.test(chitable_rhizo)
chitest_rhizo
```